Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
fix syntax of cast calculus

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. It is little changed from previous definitions.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy} \todo[inline]{The term typing rule
  for casts is broken. -Jeremy} The dynamic semantics of Blame Calculi
depend on blame strategies, so we defer them to sub-sections.

Our cast calculus extend the one in \citet{siek2009exploring} with sum types 
and product types ($ \mathtt{STLC+} $). 
Let $ S,T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P,Q $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.

>>>>

\figref{fig:blame-static} defines the syntax of cast calculus and its
static semantics. It extends the syntax in \citet{siek2009exploring} with sum 
types and product types, and annotates function codomain explicitly. 
Its semantics depend on blame strategies, so we defer them to sub-sections.
\todo[inline]{Which previous definitions are you refering to?  What
  are the little changes? -Jeremy}
\todo[inline]{Fixed -KC}
\todo[inline]{The term typing rule for casts is broken. -Jeremy}

Let $ S,T $ range over types. A type is either the dynamic type $ \star $
(a.k.a. $ \mathtt{Dyn} $, $ \mathbb{?} $, or $ \mathtt{Unknown} $), 
or a pre-type. 
Let $ P,Q $ range over pre-types. Every pre-type is a type with a type 
constructor at the top. For simplicity, we only have one base type, $ \POOunit 
$. 
Other pre-types are functions, products, and sums.
